Addition and removal energies of circular quantum dots

### 2017-09-06 Manuscript/paper.tex
Minor fix

We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.  A new technique developed by Morris et al.\ \cite{PhysRevC.92.034331} uses an alternative approach based on the Magnus expansion that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which poses a significant advantage over CC methods.  Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.

>>>>

We note that this calculation was done entirely using the traditional approach of using a high-order ODE solver to solve the flow equation.  A new technique developed by Morris et al.\ \cite{PhysRevC.92.034331} uses an alternative approach based on the Magnus expansion that obviates the need for a high-order ODE solver, leading to much more efficient computations and also allowing operators of other observables to be evolved at lower cost, which presents a significant advantage over CC methods.  Implementing this approach would allows us to study the accuracy and convergence of other possibly more sensitive observables.
